SoK: Web Application Attack Defenses (in Question)

### 2014-10-08 docs/questioning.tex
minor change

	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection \\

@@

@@

	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% & {\sc sql} injection, {\sc xss}, Buffer Overflows \\ 

>>>>

@@

	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection, {\sc xp}ath, {\sc xss} \\

@@

	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% & {\sc sql} injection, {\sc xss} \\ 
